A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-09-29 paper/paper.tex
more stuff

Since an action taken now might have repercussion long into the feature, it turns out that the
quantity to optimize is not the instantaneous rewards $r(s_t, a_t)$, a cumulative version which
takes into account the future. A standard for modeling this accumulation is the so-called
time-discounted \textit{cumulative reward} function
\begin{equation}
  \label{eq:cumr}
  R(s_t, a_t) = r(s_t, s_t) + \gamma r(s_{t+1}, s_{t+1}) +\ldots + \gamma^Tr(s_{t+T}, s_{t+T})
  = r(s_t, s_t) + \gamma \sum_{\tau=1}^{T}\gamma^{\tau-1}r(s_{t+\tau},a_{t+\tau}),
  \end{equation}
for some \textit{discount factor} $\gamma \in [0, 1]$, and horizon $T$. The choice $\gamma = 0$ (or $T=0$)  corresponds to a perfectly myopic agent who is solely concerned about their immediate rewards and have no regards for the future. For there to be any learning at all, a technical requirement is that $\gamma < 1$ \footnote{In which case we can take $T \rightarrow +\infty$, provided the reward function $r$ is bounded.}.
Thus the agent is positively biased towards considering rewards which are will
come soon. Note that $R(s_t, a_t)$ defined above is a stochastic quantity which depends on the
trajectory of a policy $\pi$,
\begin{eqnarray*}
  \begin{split}
    s_0 &\sim \mu\\
    a_0 &\sim \pi(.|s_0)\\
    s_1 &\sim \rho(.|s_0) \text{ and collect rewards }r(s_0, a_0)\\
    a_1 &\sim \pi(.|s_1)\\
    s_2 &\sim \rho(.|s_1) \text{ and collect rewards }r(s_1, a_1)\\
    \ldots\\
    a_t &\sim \pi(.|s_t)\\
    s_{t+1} &\sim \rho(.|s_t) \text{ and collect rewards }r(s_t, a_t)\\
    \ldots
  \end{split}
\end{eqnarray*}

>>>>

Since an action taken now might have repercussions long into the feature, it turns out that the
quantity to optimize is not the instantaneous rewards $r(s_t, a_t)$, a cumulative version which
takes into account the future. A standard for modeling this accumulation is the so-called
time-discounted \textit{cumulative reward} function
\begin{equation}
  \label{eq:cumr}
  R(s_t, a_t) = r(s_t, s_t) + \gamma r(s_{t+1}, s_{t+1}) +\ldots + \gamma^Tr(s_{t+T}, s_{t+T})
  = r(s_t, s_t) + \gamma \sum_{\tau=1}^{T}\gamma^{\tau-1}r(s_{t+\tau},a_{t+\tau}),
  \end{equation}
for some \textit{discount factor} $\gamma \in [0, 1]$, and horizon $T$. The choice $\gamma = 0$ (or $T=0$)  corresponds to a perfectly myopic agent who is solely concerned about their immediate rewards and have no regards for the future. For there to be any learning at all, a technical requirement is that $\gamma < 1$ \footnote{In which case we can take $T \rightarrow +\infty$, provided the reward function $r$ is bounded.}.
Thus the agent is positively biased towards considering rewards which are will
come soon. Note that $R(s_t, a_t)$ defined above is a stochastic quantity which depends on the
trajectory of a policy $\pi$,
\begin{eqnarray*}
  \begin{split}
    s_0 &\sim \mu\\
    a_0 &\sim \pi(.|s_0)\\
    s_1 &\sim \rho(.|s_0) \text{ and collect rewards }r(s_0, a_0)\\
    a_1 &\sim \pi(.|s_1)\\
    s_2 &\sim \rho(.|s_1) \text{ and collect rewards }r(s_1, a_1)\\
    \ldots\\
    a_t &\sim \pi(.|s_t)\\
    s_{t+1} &\sim \rho(.|s_t) \text{ and collect rewards }r(s_t, a_t)\\
    \ldots
  \end{split}
\end{eqnarray*}
